Turtlebot SLAM

### 2013-01-23 Article/Article.tex
works

The acquisition of these maps is a major research focus in the robotics community \cite{ Grisetti, Montemerlo02, Montemerlo, Thrun}. Building these maps relying only on noisy sensor measurements is often referred to as the Simultaneous Localization And Mapping (SLAM) problem (Subsection \ref{subsec:sotaSlam}). A large variety of solutions is available to it.
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/vacuum_cleaner.jpg}
	\caption{A vacuum cleaner robot \citep{VacuumRobot}}
	\label{fig:vacuum_cleaner}
\end{figure}

@@

\subsection{TurtleBot}
\label{subsec:turtle}
The product of this project is designed to run on a mobile robot called TurtleBot (Figure \ref{fig:turtlebot}) \citep{turtlebot}. It is a low-cost, customizable, personal robot kit. The base of the TurtleBot is an iRobot Create (A). It holds a battery pack and a 150 $degrees/second$ Single Axis Gyro. The model shown in Figure \ref{fig:turtlebot} uses a Microsoft Kinect sensor (B), the one used in this paper uses a laser range sensor, and a laptop (C) to run all the processes. The robot can also be customized using the mounting hardware (D). The robot runs on an open-source SDK based on ROS which integrates all the software needed to get the TurtleBot running. Some capabilities are included in ROS and can be used on the TurtleBot after minor configurations. These include mapping and navigation, for example. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/turtlebot.png}
	\caption{A TurtleBot \citep{turtlebot}
	\label{fig:turtlebot}
\end{figure}

@@

\subsubsection{Graph SLAM}
An intuitive way to formulate the SLAM problem is to view it as a pose graph optimization problem. Each pose along the trajectory of the robot is represented by one node. Edges are labeled with relative spatial information between the connecting nodes. This graph is built incrementally. While the robot is in motion, new nodes are added to the graph. Building up the graph, as explained above, is a straight forward procedure. The essence of the Graph SLAM method, however, is the optimization step. In this step the algorithm tries to find a spatial configuration of the trajectory which is maximally consistent with a system of constraints obtained from the edges. This problem is commonly solved using least-square error minimization techniques \citep{Grisetti}.

>>>>

The acquisition of these maps is a major research focus in the robotics community \citep{Grisetti, Montemerlo02, Montemerlo, Thrun}. Building these maps relying only on noisy sensor measurements is often referred to as the Simultaneous Localization And Mapping (SLAM) problem (Subsection \ref{subsec:sotaSlam}). A large variety of solutions is available to it.
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/vacuum_cleaner.jpg}
	\caption{A vacuum cleaner robot \citep{VacuumRobot}}
	\label{fig:vacuum_cleaner}
\end{figure}

@@

\subsection{TurtleBot}
\label{subsec:turtle}
The product of this project is designed to run on a mobile robot called TurtleBot (Figure \ref{fig:turtlebot}) \citep{turtlebot}. It is a low-cost, customizable, personal robot kit. The base of the TurtleBot is an iRobot Create (A). It holds a battery pack and a 150 $degrees/second$ Single Axis Gyro. The model shown in Figure \ref{fig:turtlebot} uses a Microsoft Kinect sensor (B), the one used in this paper uses a laser range sensor, and a laptop (C) to run all the processes. The robot can also be customized using the mounting hardware (D). The robot runs on an open-source SDK based on ROS which integrates all the software needed to get the TurtleBot running. Some capabilities are included in ROS and can be used on the TurtleBot after minor configurations. These include mapping and navigation, for example. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/turtlebot.png}
	\caption{A TurtleBot \citep{turtlebot}}
	\label{fig:turtlebot}
\end{figure}

@@

\subsubsection{Graph SLAM}
An intuitive way to formulate the SLAM problem is to view it as a pose graph optimization problem. Each pose along the trajectory of the robot is represented by a node. Edges are labeled with relative spatial information between the connecting nodes. This graph is built incrementally. While the robot is in motion, new nodes are added to the graph. Building up the graph, as explained above, is a straight forward procedure. The essence of the Graph SLAM method, however, is the optimization step. In this step the algorithm tries to find a spatial configuration of the trajectory which is maximally consistent with a system of constraints obtained from the edges. This problem is commonly solved using least-square error minimization techniques \citep{Grisetti}.
